---
title: "List of models"
output: 
  github_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library("tidyverse")
library("R6")
library("jsonlite")

modelListGenerator <- R6Class(
  "modelListGenerator",
  public = list(
    data = NULL,
    initialize = function() {
      invisible(self)
    },
    add = function(Model, Function = "", Basis_function = "", Notes = "") {
      row <- tibble(Model = Model, Function = Function, Basis_function = Basis_function,
                    Notes = Notes)
      if (is.null(self$data)) {
        self$data <- row
      } else {
        self$data <- bind_rows(self$data, row) 
      }
      invisible(self)
    },
    print = function(...) {
      print(self$data)
      invisible(self)
    },
    table = function(...) {
      print(knitr::kable(self$data, ...))
      invisible(self)
    }
  )
)
```

```{r, results='asis'}
model_table <- modelListGenerator$new()
model_table$add("Auto ARIMA", "`auto_arima_forecast`", "`forecast::auto.arima`")
model_table$add("Mean", "`constan_mean_forecast`", "`forecast::Arima(c(0,0,0))`")
model_table$add("ETS", "`ets_forecast`", "`forecast::ets()`", Notes = "auto add/mult order, auto damped")
model_table$add("RW", "`rw_forecast`", "`forecast::rwf()`", "flexible lambda")
model_table$add("RW-DRIFT", "`rw_drift_forecast`", "`forecast::rwf(drift = TRUE)`")
model_table$add("RW-SEAS", "`rw_seasonal_forecast`", "`forecast::snaive()`")
model_table$add("arithmetic RW", "`arithmetic_rw_forecast`", "`forecast::Arima(c(0, 1, 0), lambda = NULL)`")
model_table$add("geometric RW", "`geometric_rw_forecast`", "`forecast::Arima(c(0, 1, 0), lambda = 0)`", Notes = "Values >0 only")
model_table$add("NNAR")
model_table$add("TBATS")
model_table$add("STLM-AR")
model_table$add("DS-RW", "`rw_deseasoned_forecast`", Notes = "RW on de-seasoned data")
model_table$add("DS-SES", "`ses_deseasoned_forecast`", Notes = "same as ets(\"ANN\") on de-seasoned data")
model_table$add("DS-holt", Notes = "same as ets(\"AAN\") on de-seasoned data")
model_table$add("DS-holt-damped", Notes = "same as ets(\"AAN\", damped = TRUE) on de-seasoned data")
model_table$add("THETAF")
model_table$add("M4_Comp", Notes = "M4 benchmark composite")
model_table$add("M4_Meta", Notes = "M4 meta learning composite")

model_table$table()
```

## M4 competition

The benchmark and second place winner in the M4 competition were ensemble models that would not be too hard to integrate. And the benchmark is very simple, would not be difficult at all.

Competition benchmark: raw code at https://github.com/M4Competition/M4-methods/blob/master/Benchmarks%20and%20Evaluation.R, it is a combination f4, 5, and 6, which are plain exponential smoothing models on deseasoned data. 

Hyndman et all have a M4 meta learning model, basically 9 plain time series models whose ensemble weights are determined by xgboost using a broad range of extra time series features extracted as features for the meta model. See here https://github.com/robjhyndman/M4metalearning/blob/master/R/forec_methods_list.R and here https://github.com/M4Competition/M4-methods/blob/master/245%20-%20pmontman/M4-Method-Description.pdf. 

The 3 and 9 component models for the benchmark and M4_meta model are already included in the list above. 

### Competition benchmark models

```r
SeasonalityTest <- function(input, ppy){
  #Used to determine whether a time series is seasonal
  tcrit <- 1.645
  if (length(input)<3*ppy){
    test_seasonal <- FALSE
  }else{
    xacf <- acf(input, plot = FALSE)$acf[-1, 1, 1]
    clim <- tcrit/sqrt(length(input)) * sqrt(cumsum(c(1, 2 * xacf^2)))
    test_seasonal <- ( abs(xacf[ppy]) > clim[ppy] )
    
    if (is.na(test_seasonal)==TRUE){ test_seasonal <- FALSE }
  }
  
  return(test_seasonal)
}

Benchmarks <- function(input, fh){
  #Used to estimate the statistical benchmarks of the M4 competition
  
  #Estimate seasonaly adjusted time series
  ppy <- frequency(input) ; ST <- F
  if (ppy>1){ ST <- SeasonalityTest(input,ppy) }
  if (ST==T){
    Dec <- decompose(input,type="multiplicative")
    des_input <- input/Dec$seasonal
    SIout <- head(rep(Dec$seasonal[(length(Dec$seasonal)-ppy+1):length(Dec$seasonal)], fh), fh)
  }else{
    des_input <- input ; SIout <- rep(1, fh)
  }
  
  f1 <- naive(input, h=fh)$mean #Naive
  f2 <- naive_seasonal(input, fh=fh) #Seasonal Naive
  f3 <- naive(des_input, h=fh)$mean*SIout #Naive2
  f4 <- ses(des_input, h=fh)$mean*SIout #Ses
  f5 <- holt(des_input, h=fh, damped=F)$mean*SIout #Holt
  f6 <- holt(des_input, h=fh, damped=T)$mean*SIout #Damped
  f7 <- Theta.classic(input=des_input, fh=fh)$mean*SIout #Theta
  f8 <- (f4+f5+f6)/3 #Comb
  
  return(list(f1,f2,f3,f4,f5,f6,f7,f8))
}
```

## Example forecasts

```{r example-forecasts, warning = FALSE, fig.height=3, results = 'asis'}
output_files <- dir("../tests/io", pattern = "models_[0-9]+_output.json", full.names = TRUE)

error_plot <- function(target, cutpoints, model_string, error_message) {
  x_pos <- as.Date(target$date[1] + diff(range(target$date)) / 2)
  y_pos <- (max(target$value, na.rm = TRUE) + mean(target$value, na.rm = TRUE)) / 2
  p <- ggplot(target, aes(x = date, y = value)) +
    geom_hline(yintercept = cutpoints, linetype = 3) +
    geom_line() +
    theme_minimal() +
    ggtitle(model_string) +
    labs(x = "", y = "") +
    annotate("text", x = x_pos, y = y_pos, col = "gray50",
              label = error_message %>% str_wrap())
  p
}

for (of in output_files) {
  output <- read_json(of, simplifyVector = TRUE)
  target <- output$parsed_request$target %>%
    as_tibble() %>%
    mutate(date = as.Date(date))
  cutpoints <- output$parsed_request$separations$cutpoints %>% head(-1) %>% tail(-1)
  
  cat(sprintf("\n\n### %s\n\n", output$parsed_request$ifp_name))
  
  for (ff in sort(names(output$forecasts))) {
    forecast_data <- output$forecasts[[ff]]
    
    if (!is.null(forecast_data$estimated)) {
      
      p <- error_plot(target, cutpoints, forecast_data$model, forecast_data$r_error_message)
      
    } else {
      
      ts_fcast <- forecast_data$ts %>%
      as_tibble() %>%
      setNames(forecast_data$ts_colnames) %>%
      mutate(date = as.Date(date)) %>%
      mutate_at(vars(-date), as.numeric)
    
    df <- bind_rows(target, ts_fcast)
    
    p <- ggplot(df, aes(x = date)) +
        geom_line(aes(y = value)) + 
        theme_minimal() +
        ggtitle(sprintf("%s", ff),
                subtitle = forecast_data$internal$mdl_string) +
        labs(x = "", y = "") +
        geom_hline(yintercept = cutpoints, linetype = 3)
    p <- p + 
        geom_ribbon(aes(ymin = `Lo 95`, ymax = `Hi 95`), fill = "lightblue") +
        geom_line(aes(y = `Point Forecast`), color = "blue")
    
    }
    
    print(p)
    cat("\n\n")
    
  }
}
```

